Document Embedding for Scientific Articles:\newline A validation of word embeddings

### 2018-07-25 Paper/paper.tex
mac sync

Table~\ref{table:computationTimes} shows the computation time needed for 1.000 distance calculations, based on the cosine-similarity distance measurement. 1.000 vectors (V) have been randomly selected and transformed into a matrix (M). We then calculate the distance between each vector from V to the matrix M; this results in the distance between the vector an all vectors (V) contained in the matrix (M). We do this for all vectors in V, for the 10K/10K TF-IDF set and the default embeddings. Because the embeddings are dense vectors, we also transformed the TF-IDF feature vectors to dense vectors for this comparison. Table~\ref{table:computationTimes} shows both computation time in seconds and the embedding fraction; meaning how many times faster the embedding is, based on time in seconds.

>>>>

Table~\ref{table:computationTimes} shows the computation time needed for 1.000 distance calculations, based on the cosine-similarity distance measurement. 1.000 vectors (V) have been randomly selected and transformed into a matrix (M). We then calculate the distance between each vector from V to the matrix M; this results in the distance between the vector an all vectors (V) contained in the matrix (M). We do this for all vectors in V, for the 10K/10K TF-IDF set and the default embeddings. Because the embeddings are dense vectors, we also transformed the TF-IDF feature vectors to dense vectors for this comparison. Table~\ref{table:computationTimes} shows both computation time in seconds and the embedding fraction; meaning how many times more efficient the embedding is for online similarity calculation, based on time in seconds.
